Capstone Movielens Report

### 2025-12-28 reports/capstone-movielens.site/02.5.UME-model.Rmd

The following [piece of code](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L571) performs this operation:
```{r  main-script@l571, eval=FALSE}
lambdas <- seq(0, 1, 0.1)
cv.UME.preset.result <- 
  tune.model_param(lambdas, regularize.test_lambda.UM_effect.cv)

@@

The following [code snippet](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L608) prepares the interval of values for the $\lambda$ parameter, over which the operation has to be done:
```{r  main-script@l608, eval=FALSE}
endpoints <- 
  get_fine_tune.param.endpoints(cv.UME.preset.result$tuned.result)

@@

And the next [piece of code](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L617) below accomplishes the task of *fine-tuning* the model:
```{r  main-script@l617, eval=FALSE}
UME.rglr.fine_tune.cache.base_name <- "UME.rglr.fine-tune"

>>>>

The following [code snippet](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L571) performs this operation:
```{r main-script@l571, eval=FALSE}
lambdas <- seq(0, 1, 0.1)
cv.UME.preset.result <- 
  tune.model_param(lambdas, regularize.test_lambda.UM_effect.cv)

@@

The following [piece of code](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L608) prepares the interval of values for the $\lambda$ parameter, over which the operation has to be done:
```{r main-script@l608, eval=FALSE}
endpoints <- 
  get_fine_tune.param.endpoints(cv.UME.preset.result$tuned.result)

@@

And the next [code snippet](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L617) below accomplishes the task of *fine-tuning* the model:
```{r main-script@l617, eval=FALSE}
UME.rglr.fine_tune.cache.base_name <- "UME.rglr.fine-tune"
